https://www.overleaf.com/4447223514mbvjsgnxnvgv Quantifying the importance of an inference model in Bayesian phylogenetics

### 2019-10-02 content.tex
Proper glory to @Giappo

RJCB, GL and RSE conceived the idea for the package. 
RJCB created and tested the package, and wrote the first draft of the manuscript.
GL tested the package and contributed to revisions.
RSE contributed to revisions.

>>>>

RJCB, GL and RSE conceived the idea for the package. 
RJCB created, tested and revised the package.
GL done major contributions to the package.
RJCB wrote the first draft of the manuscript, 
GL and RSE contributed to revisions.
